%спіс скарыстанай крыніц

\sectionWithoutNumber{Спіс скарыстаных крыніц}

\begin{enumerate}[{label=\arabic{*}}]

    \item Effective DevOps:
          Building a Culture of Collaboration, Affinity,
          and Tooling at Scale / O'Reilly Media. –
          Jennifer Davis, Katherine Daniels, 2016.
        \label{book:Effective Devops}

    \item DevOps and AWS [Электронны рэсурс]. --
          Рэжым доступу : https://\-aws.amazon.com/ devops/. --
          Дата доступу : 01.05.2019.
        \label{site:aws.amazon.com/devops}

    \item DevOps [Электронны рэсурс]. --
          Рэжым доступу : https://ru.wikipedia.org/wiki/DevOps.\,\,--
          Дата доступу : 01.05.2019.
        \label{site:ru.wikipedia.org/wiki/devops}

    \item Challenges in Adopting a Devops Approach
          to Software Development and Operations : Thesis / 
          Aalot-yliopisto. -- Joonas Hamunen, 2016.
        \label{article:Challenges in Adopting a Devops}

    \item DevOps: A Software Architect's Perspective /
          Addison-Wesley Professional. --
          Len Bass, Ingo Weber, Liming Zhu, 2015.
        \label{book:DevOps: A Software Architect's Perspective}

    \item Lean Enterprise:
          How High Performance Organizations Innovate at Scale /
          O'Reilly Media. --
          Jez Humble, Joanne Molesky, 2015.
        \label{book:Lean Enterprise}
 
    \item Lean Software Development: An Agile Toolkit /
          Addison-Wesley Professional. --
          Mary Poppendieck, Tom Poppendieck, 2003.
        \label{book:Lean Software Development}

    \item 15 Metrics for DevOps Success [Электронны рэсурс]. -- 
          Рэжым доступу : \\
          https://stackify.com/15-metrics-for-devops-success/. --
          Дата доступу : 01.05.2019.
        \label{site:stackify.com/15-metrics}

    \item 2015 State of DevOps Report
          Рэжым доступу : https://puppet.com/resources/whitepaper/
          2015-state-devops-report. --
          Дата доступу : 01.05.2019.
        \label{site:puppet.com/resources/whitepaper/2015}

    \item DevOps: The Worst-Kept Secret to Winning
          in the Application Economy : Databook /
          Research paper. --
          CA technologies, 2014.
        \label{article:DevOps:The Worst-Kept Secret}

    \item Continuous Integration:
          Improving Software Quality and Reducing Risk /
          Addison-Wesley Professional. --
          Paul Duvall, Stephen M. Matyas III, Adrew Glover, 2007.
        \label{book:Continuous Integration}

    \item Continuous Delivery: 
          Reliable Software Releases through Build, Test, 
          and Deployment Auto\-mation / 
          Addison-Wesley Professional. -- 
          Jez Humble, David Farley, 2010.
        \label{book:Continuous Delivery}

    \item Continuous Delivery Vs. Continuous Deployment: What's the Diff?
          [Электронны рэсурс].\,\,--
          Рэжым доступу : https://puppetlabs.com/blog/continuous-delivery-vs-continuous-deployment-whats-diff. --
          Дата доступу : 01.05.2019.
        % гэта веб-сайт, а не кніга
        \label{book:Continuous Delivery vs. Continuous Deployment}

    \item How to build a modern CI/CD pipeline
          [Электронны рэсурс]. --
          Рэжым доступу : \\
          https://medium.com/bettercode/how-to-build-a-modern-ci-cd-pipeline-5faa01891a5b. --
          Дата доступу : 01.05.2019.
        \label{site:CI/CD-pipeline}

    \item OS-level virtualisation
          [Электронны рэсурс]. --
          Рэжым доступу : \\
          https://en.wikipedia.org/wiki/OS-level\_virtualisation --
          Дата доступу : 08.05.2019.
        \label{site:OS-level}

    \item Top DevOps Tools
          [Электронны рэсурс]. --
          Рэжым доступу : \\
          https://stackify.com/top-devops-tools. --
          Дата доступу : 09.05.2019.
        \label{site:Top DevOps Tools}
\end{enumerate}
